An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-10-05 latex_files/ch2/2-3-ROMC.tex
reordered files and fixed graph colors

\subsubsection*{Estimating the acceptance regions}
The acceptance region $\accregioni$ is approximated by a bounding box
$\accregionihat$ around it. Ideally, we want the bounding box to be as
tight as possible to $\mathcal{S}_i$, to ensure high acceptance rate
in the importance sampling, and big enough for not discarding valid
parts of $\mathcal{S}_i$. \TODO{did remove the issue of disconnected
sets; which needed to be handled by multiple restarts with the same
seed. Is this something that the code would support? It's expensive
because we don't know when we need it! I think it's an open research
question, not related to this software paper, so I omitted it.} The
bounding boxes are built in two steps. First, we define their axes
$\mathbf{v}_d$ based on the (estimated) curvature of the distance
$\thetab_i^*$, second, we determine the size of the box via a
one-dimensional line-search method along each axix, see
Algorithm~\ref{alg:region_construction} for the details. After the
bounding boxes construction, a uniform distribution $q_i$ is defined
on each bounding box, and is used as the proposal region for
importance sampling.

>>>>

\subsubsection*{Estimating the acceptance regions}
The acceptance region $\accregioni$ is approximated by a bounding box
$\accregionihat$ around it. Ideally, we want the bounding box to be as
tight as possible to $\mathcal{S}_i$, to ensure high acceptance rate
in the importance sampling, and big enough for not discarding valid
parts of $\mathcal{S}_i$. The bounding boxes are built in two
steps. First, we define their axes $\mathbf{v}_d$ based on the
(estimated) curvature of the distance $\thetab_i^*$, second, we
determine the size of the box via a one-dimensional line-search method
along each axix, see Algorithm~\ref{alg:region_construction} for the
details. After the bounding boxes construction, a uniform distribution
$q_i$ is defined on each bounding box, and is used as the proposal
region for importance sampling.

### 2021-10-05 latex_files/ch3/3-0-design-principles.tex
reordered files and fixed graph colors

For designing an extendable implementation of ROMC, we firstly define
ROMC as a sequence of algorithmic steps. The algorithmic view of ROMC
serves as the driver for the implementation at \pkg{ELFI}. At a high
level, ROMC can be split into the training and the inference part. In
general terms, the training part covers all steps for estimating the
proposal regions and the inference part for getting weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-10 (before the vertical line) form the training part, while
steps 12-17 the inference part.

@@

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions $\mathcal{\hat{S}}_i$. The tasks are; (a) sampling
the nuisance variables $\vb_i \sim p(\vb)$ for obtaining the
deterministic functions $d_i(\thetab)$, (b) defining the optimisation
problems $\min_{\thetab} \: d_i(\thetab)$, (c) obtaining
$\thetab_i^*$, $d_i^*$ (d) checking whether $d_i^* \leq \epsilon$ and
(e) computing the proposal distribution $q_i$. If $d_i(\thetab)$ is
differentiable, using a gradient-based method is advised for obtaining
$\thetab_i^*$ faster. In case $\nabla_{\thetab} d_i$ is available in
closed-form, the procedure is upgraded in terms of both accuracy and
efficiency. If closed-form description is not available, gradients
approximation with finite-differences requires two evaluations of
$d_i$ for \emph{each} parameter $\theta_d$, which can only work in
low-dimensional problems. If $d_i(\thetab)$ is not differentiable, the
Bayesian Optimisation can be used as an alternative solution. In this
scenario, the training part becomes slower due to fitting of the
surrogate model and the blind optimisation steps. After obtaning the
optimal points $\thetab^*$, the training part gets completed by
estimating the proposal regions;
Algorithm~\ref{alg:region_construction} describes the line search
approach for finding the region's boundaries.

>>>>

For designing an extendable implementation of ROMC, we firstly define
ROMC as a sequence of algorithmic steps. The algorithmic view of ROMC
serves as the driver for the implementation at \pkg{ELFI}. At a high
level, ROMC can be split into the trainind the inference part. In
general terms, the training part covers all steps for estimating the
proposal regions and the inference part for getting weighted
samples. Algorithm~\ref{alg:romc_algorithm} defines ROMC formally;
Steps 2-10 (before the vertical line) form the training part, while
steps 12-17 the inference part.

@@

\subsubsection*{Training part}
\noindent
At the training (fitting) part, the goal is the estimation of the
proposal regions $\mathcal{\hat{S}}_i$. The tasks are; (a) sampling
the nuisance variables $\vb_i \sim p(\vb)$ for obtaining the
deterministic functions $d_i(\thetab)$, (b) defining the optimisation
problems $\min_{\thetab} \: d_i(\thetab)$, (c) obtaining
$\thetab_i^*$, $d_i^*$ (d) checking whether $d_i^* \leq \epsilon$ and
(e) computing the proposal distribution $q_i$.

If $d_i(\thetab)$ is differentiable, using a gradient-based method is
advised for obtaining $\thetab_i^*$ faster. In this case, the
gradients $\nabla_{\thetab} d_i$ gradients are approximated
automatically with finite-differences. This procedure requires about
two evaluations of $d_i$ for \emph{each} parameter $\theta_d$, which
can only work in low-dimensional problems. If $d_i(\thetab)$ is not
differentiable, the Bayesian Optimisation can be used as an
alternative solution. In this scenario, the training part becomes
slower due to fitting of the surrogate model and the blind
optimisation steps.

After obtaining the optimal points $\thetab^*$, the training part gets
completed by estimating the proposal
regions. Algorithm~\ref{alg:region_construction} describes the line
search approach for finding the region's boundaries. An important step
for the proposal region estimation is deciding the axes of the
bounding box i.e. the directions $\vb_d$ we follow for reaching the
boundaries. We approximate them as the direction of the highest
curvature of $d_i$ at $\thetab_i^*$. This estimation is given by the
eigenvalues of the Hessian matrix $\hessian_i$ of
$d_i$\footnote{Either the real distance $d_i$ or the Gaussian Process
  approximation $\hat{d}_i$} at $\thetab_i$. The Hessian matrix is
approximated numerically. In case where the distance function is the
Euclidean, the Hessian matrix can be also computed as
$\hessian_i = \jac_i^T\jac_i$, where $\jac_i$ is the Jacobian matrix
of the summary statistics $\Phi(M_d(\thetab, \vb=\vb_i))$ at
$\thetab_i^*$. The approximation through the Jacobian matrix has the
computational advantage of using only first-order derivatives.

### 2021-10-05 latex_files/ch4/4-2-inference.tex
reordered files and fixed graph colors

The inference part contains in four methods.

@@

\noindent
This is the basic inference utility of the ROMC implementation; we
draw $n_2$ samples for each bounding box region. This gives a total of
$k \times n_2$, where $k < n_1$ is the number of the optimal points
remained after filtering\footnote{From the $n_1$ optimisation
  problems, only the ones with $g_i(\thetab_*) < \epsilon$ are
  maintained for building a bounding box}. The samples are drawn from
a uniform distribution $q_i$ defined over the corresponding bounding
box and the weight $w_i$ is computed as in
equation~\eqref{eq:sampling}.

>>>>

The inference part contains four methods.

@@

\noindent
This is the basic inference utility of the ROMC implementation; we
draw $n_2$ samples for each bounding box region. This gives a total of
$k \times n_2$, where $k < n_1$ is the number of the optimal points
remained after filtering\footnote{From the $n_1$ optimisation
  problems, only the ones with $d_i(\thetab_*) < \epsilon$ are
  maintained for building a bounding box}. The samples are drawn from
a uniform distribution $q_i$ defined over the corresponding bounding
box and the weight $w_i$ is computed as in
algorithm~\ref{alg:sampling_GB}.

### 2021-10-05 latex_files/ch4/4-3-evaluation.tex
reordered files and fixed graph colors

  nof_samples = len(romc.result.weights)
  ess = romc.compute_ess()
  print("Nof Samples: %d, ESS: %.3f" % (nof_samples, ess))
  # Nof Samples: 19950, ESS: 16694.816
----------------------------------------------------------------------------  
\end{Code}

>>>>

  nof_samples = len(romc.result.weights)
  ess = romc.compute_ess()
  print("Nof Samples: %d, ESS: %.3f" % (nof_samples, ess))
  # Nof Samples: 19300, ESS: 16138.825
----------------------------------------------------------------------------  
\end{Code}

### 2021-10-05 latex_files/ch5/5-1-ma2.tex
reordered files and fixed graph colors

As in the previous example, we perform the inference using both
optimisation alternatives (gradient-based and Bayesian optimisation)
and we compare the results at each step. In the end, we use the
Rejection ABC algorithm for evaluating both approximations. Rejection
ABC is a robust method in terms of accuracy and can be used for
baseline comparison.

In figure \ref{fig:ma2_5}, we illustrate the acceptance region of the
same deterministic simulator, i.e. with \code{seed=799981517}, in the
gradient-based and the Bayesian optimisation case. The acceptance
regions are similar in both cases. The optimal points are close and
the search directions are similar. This indicates that both
optimization scemes work robustly. Therefore, we observe that as we
move away from the optimal pint, the surrogate model fitted by the
Bayesian Optimisation tends to deviate from the real distance. This
divergence affects the bounding box approximation and explains some
small differences between the posterior approximations, as shown in
figure \ref{fig:ma2_3}. In figure \ref{fig:ma2_3}, we demonstrate the
histograms of the marginal posteriors, using the three different
methods; (a) Rejection ABC (first line), (b) ROMC with gradient-based
optimisation (second line) and (c) ROMC with Bayesian optimisation
(third line). Undoubtedly, we observe that there is a significant
similarity between the three approaches. The Rejection ABC inference
has been set to infer 10000 accepted samples, with threshold
$\epsilon=0.1$. At table \ref{tab:ma2} we present the empirical mean
$\mu$ and standard deviation $\sigma$ for each inference approach, for
verifying their agreement.

\begin{center} \label{tab:ma2}
\begin{tabular}{ c|c|c|c|c }
\hline
& $\mu_{\theta_1}$ & $\sigma_{\theta_1}$ & $\mu_{\theta_2}$ & $\sigma_{\theta_2}$ \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.07 & 0.172 \\
\hline
ROMC (gradient-based) & 0.504 & 0.143 & 0.033 & 0.171 \\
\hline
ROMC (Bayesian optimisation) & 0.502 & 0.166 & 0.079 & 0.168 \\
\hline
\end{tabular}
\end{center}

@@

% \begin{figure}[h]
%     \begin{center}
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t1_rejection.png}
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t2_rejection.png}\\
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t1_romc.png}
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t2_romc.png}\\
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t1_romc_bo.png}
%       \includegraphics[width=0.35\textwidth]{./latex_files/images/chapter4/mae2_hist_t2_romc_bo.png}\\
%     \end{center}
%     \caption[MA2 example, evaluation of the marginal
%     distributions.]{Histogram of the marginal posterior distributions
%       using three different inference approaches; (a) in the first
%       row, the samples are obtained using Rejection ABC sampling (b)
%       in the second row, using ROMC with a gradient-based optimiser
%       and (c) in the third row, using ROMC with Bayesian optimization
%       approach. The vertical (red) line represents the samples mean
%       $\mu$ and the horizontal (black) the standard deviation
%       $\sigma$.}
%   \label{fig:ma2_3}
% \end{figure}

\begin{figure}[ht]
  \begin{center}
    \input{./latex_files/images/chapter4/mae2_hist_t1_rejection.tex}
    \input{./latex_files/images/chapter4/mae2_hist_t2_rejection.tex}\\
    \input{./latex_files/images/chapter4/mae2_hist_t1_romc.tex}
    \input{./latex_files/images/chapter4/mae2_hist_t2_romc.tex}\\
    \input{./latex_files/images/chapter4/mae2_hist_t1_romc_bo.tex}
    \input{./latex_files/images/chapter4/mae2_hist_t2_romc_bo.tex}\\
    \end{center}
    \caption[MA2 example, evaluation of the marginal
    distributions.]{Histogram of the marginal posterior distributions
      using three different inference approaches; (a) in the first
      row, the samples are obtained using Rejection ABC sampling (b)
      in the second row, using ROMC with a gradient-based optimiser
      and (c) in the third row, using ROMC with Bayesian optimization
      approach. The vertical (red) line represents the samples mean
      $\mu$ and the horizontal (black) the standard deviation
      $\sigma$.}
  \label{fig:ma2_3}
\end{figure}

% \begin{figure}[H]
%     \begin{center}
%       \includegraphics[width=0.48\textwidth]{./latex_files/images/chapter4/mae2_romc_posterior.png}
%       \includegraphics[width=0.48\textwidth]{./latex_files/images/chapter4/mae2_romc_posterior_bo.png}
%     \end{center}
%     \caption[MA2 example, approximate posterior.]{ROMC approximate posteriors using gradient-based approach
%       (left) and Bayesian optimisation approach (right).}
%   \label{fig:ma2_4}
% \end{figure}

>>>>

As in the previous example, we perform the inference using both
optimisation alternatives (gradient-based and Bayesian optimisation)
and, in the end, by extending the implementation with a Neural Network
surrogate model. In the end, we use the Rejection ABC algorithm for
evaluating our approaches; Rejection ABC is a robust method in terms
of accuracy and can be used for baseline comparison.

The implementation's extension is performed using a multi-layer
perceptron as local surrogate function, as illustrated in chapter
... This intervention can be done easily by coding a custom
optimisation function with the surrogate model of our own
preference. The surrogate model substitutes the real distance function
$d_i$ inside the proposal region $q_i \quad \forall i$ at the
inference phase i.e. sampling, computing an expectation and evaluating
the posterior. In our example we use a neural network of two hidden
layers of 10 neurons each and we train it in 500 examples for each
proposal region.

In figure \ref{fig:ma2_5}, we illustrate the acceptance region of the
same deterministic simulator, in the gradient-based and the Bayesian
optimisation case. The acceptance regions are similar even though the
optimal points differ significantly due to the different optimisation
schemens.

In figure \ref{fig:ma2_3}, we demonstrate the histograms of the
marginal posteriors, using all four approaches; (a) Rejection ABC
(first column), (b) ROMC with gradient-based optimisation (second
column) (c) ROMC with Bayesian optimisation (third column) and (d)
ROMC with the Neural Network extendion. We observe that there is a
significant aggreement between the different approaches. The Rejection
ABC inference has been set to infer 10000 accepted samples, with
threshold $\epsilon=0.1$. At table \ref{tab:ma2} we present the
empirical mean $\mu$ and standard deviation $\sigma$ for each
inference approach. In figure \ref{fig:ma2_4}, we illustrate the
unnormalized posterior for the three different variations of the ROMC
method.

\subsubsection*{Extending the implementation}

\begin{center} \label{tab:ma2}
\begin{tabular}{ c|c|c|c|c }
\hline
& $\mu_{\theta_1}$ & $\sigma_{\theta_1}$ & $\mu_{\theta_2}$ & $\sigma_{\theta_2}$ \\
\hline \hline
Rejection ABC & 0.516 & 0.142 & 0.07 & 0.172 \\
\hline
ROMC (gradient-based) & 0.503 & 0.143 & 0.032 & 0.17 \\
\hline
ROMC (Bayesian optimisation) & 0.494 & 0.16 & 0.086 & 0.167 \\
\hline
ROMC (Neural Network) & 0.503 & 0.140 & 0.03 & 0.171 \\
\hline
\end{tabular}
\end{center}

@@

\begin{figure}[ht]
  \begin{center}
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t1_rejection.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t1_romc.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t1_romc_bo.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t1_romc_nn.tex}
    }\\
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t2_rejection.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t2_romc.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t2_romc_bo.tex}
    }
    \resizebox{.24\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_hist_t2_romc_nn.tex}
    }
    \end{center}
    \caption[MA2 example, evaluation of the marginal
    distributions.]{Histogram of the marginal posterior distributions
      using three different inference approaches; (a) in the first
      row, the samples are obtained using Rejection ABC sampling (b)
      in the second row, using ROMC with a gradient-based optimiser
      and (c) in the third row, using ROMC with Bayesian optimization
      approach. The vertical (red) line represents the samples mean
      $\mu$ and the horizontal (black) the standard deviation
      $\sigma$.}
  \label{fig:ma2_3}
\end{figure}

\begin{figure}[ht]
  \begin{center}
    \resizebox{.32\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_romc_posterior.tex}
    }
    \resizebox{.32\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_romc_posterior_bo.tex}
    }
    \resizebox{.32\columnwidth}{!}{%
      \input{./latex_files/images/chapter4/mae2_romc_posterior_nn.tex}
    }
    \end{center}
    \caption[MA2 example, posterior distribution.]{The unnormalized posterior distribution using the ROMC method with (a) a gradient-based optimization (b) Bayesian Optimization (c) gradient-based with a Neural Network as a surrogate model.}
  \label{fig:ma2_4}
\end{figure}

### 2021-10-05 latex_files/ch5/5-2-execution-time.tex
reordered files and fixed graph colors

As already stated, it is straightforward for the two basic parts of
the training part to be parallelised. There is a batch of $n_1$
independent objectives functions to be optimised and $n_1$ bounding
boxes to be built. Both tasks can be applied in a parallel utilizing
all the available CPU cores. Our implementation supports
parallelization using the built-in \proglang{Python}
\pkg{multiprocess}. In figure \label{fig:exec_parallel} we observe the
execution times for performing the inference. The parallel version
performs all tasks between 2.5 and 6 times faster compared to the
sequential. Optimisation problems are solved almost 6 times
faster. Sampling is executed 3.5 times faster, whereas evaluating the
posterior and constructing the bounding boxes almost 2.5 times faster.

\begin{figure}[ht] \label{fig:exec_parallel}
  \centering
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Solve optimization problems},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Proposal regions},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Sample},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Evaluate posterior},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \caption[Execution time exploiting parallelisation]{In the first
      line, we compare the parallel and sequential execution of the
      training part and at the second line the inference part. At the
      left figure, we measure the execution time for sampling $n_2=50$
      points per region. At the right figure we measure the execution
      time for evaluating the posterior at a batch of $50$ points.}
\end{figure}

>>>>

As already stated, it is straightforward for the two basic parts of
the training part to be parallelised. There is a batch of $n_1$
independent objectives functions to be optimised and $n_1$ bounding
boxes to be built. Both tasks can be applied in a parallel utilizing
all the available CPU cores. Our implementation supports
parallelization using the built-in \proglang{Python} package
\pkg{multiprocess}. In figure~\ref{fig:exec_parallel} we observe the
execution times for performing the inference. The parallel version
performs all tasks between 2.5 and 6 times faster compared to the
sequential. Optimisation problems are solved almost 6 times
faster. Sampling is executed 3.5 times faster, whereas evaluating the
posterior and constructing the bounding boxes almost 2.5 times faster.

\begin{figure}[ht]
  \centering
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Solve optimization problems},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Proposal regions},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Sample},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \begin{minipage}[t]{.49\textwidth}
      \begin{tikzpicture}
        \begin{axis}[
          title={Evaluate posterior},
          xlabel={$n_1$},
          ylabel={seconds},
          xmin=1, xmax=500,
          ymin=0, ymax=7,
          xtick={1,100,200,300,400,500},
          ytick={0, 1, 2, 3, 4, 5, 6, 7},
          legend pos=north west,
          ymajorgrids=true,
          grid style=dashed,
          ]
          \addplot[color=blue, mark=o] coordinates {
            (1,0.05)(125,1.6)(250,3.5)(375,5)(500,6.8)
          };
          \addlegendentry{sequential}
          \addplot[color=red, mark=o] coordinates {
            (1,0.2)(125,0.6)(250,1)(375,1.5)(500,2)
          };
          \addlegendentry{parallel}          
        \end{axis}
      \end{tikzpicture}
    \end{minipage}\hfill
    \caption[Execution time exploiting parallelization]{In the first
      line, we compare the parallel and sequential execution of the
      training part and at the second line the inference part. At the
      left figure, we measure the execution time for sampling $n_2=50$
      points per region. At the right figure we measure the execution
      time for evaluating the posterior at a batch of $50$ points.}
      \label{fig:exec_parallel}
\end{figure}

### 2021-10-05 latex_files/graphs/romc_graph.tex
reordered files and fixed graph colors

\begin{figure}[ht]
  \begin{center}
  %   \resizebox{.32\textwidth}{!}{
  %     \begin{tikzpicture}[node distance=1.4cm, scale=.1]
  %     \end{tikzpicture}
  %   }
    \resizebox{.8\textwidth}{!}{    
      \begin{tikzpicture}[node distance=1.2cm, scale=.1]
        % first graph
        % private functions
        \node (n1) [train_process, xshift=-.8cm] { $\_sample\_nuisance()$  };
        \node (n2) [train_process, below of=n1] { $\_define\_objectives()$  };
        \node (n3) [decision, below of=n2, yshift=-.5cm] { $grads?$  };
        \node (n4) [train_process, left of=n3, yshift=-1cm, xshift=-1.5cm] { $\_solve\_gradients()$  };
        \node (n5) [train_process, right of=n3, yshift=-1cm, xshift=1.5cm] { $\_solve\_bo()$  };
        \node (n6) [train_process, below of=n3, yshift=-1.5cm] { $\_filter\_solutions()$  };
        \node (n7) [train_process, below of=n6] { $\_build\_boxes()$  };
        \node (n8) [decision, below of=n7] { $fit?$  };
        \node (n9) [train_process, right of=n8, yshift=-1cm, xshift=1cm] { $\_fit\_models()$  };

@@

        % add headers
        \node (algorithm) [below of=n1, yshift=2.5cm, xshift=1cm, minimum width=4cm, minimum height=1cm] {\huge{Implementation Design} };

        % backgrounds
        \draw [ultra thick, draw=black, fill=yellow, opacity=0.15, rounded corners=20pt] (-115,8) rectangle (70, -108);

        \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-115,8) rectangle (57, -48);
        \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-115,-50) rectangle (57, -108);

        \draw [ultra thick, draw=black, fill=green, opacity=0.15, rounded corners=20pt] (-115,-110) rectangle (70, -140);

        \draw [ultra thick, draw=black, fill=cyan, opacity=0.15, rounded corners=20pt] (-115,-142) rectangle (70, -160);

        \draw [ultra thick, draw=black, fill=magenta, opacity=0.05, rounded corners=20pt] (-115,18) rectangle (-64, -160);

        \draw [ultra thick, draw=black, fill=magenta, opacity=0.05, rounded corners=20pt] (-60,18) rectangle (70, -160);

@@

        % % backgrounds
        % \draw [ultra thick, draw=black, fill=yellow, opacity=0.15, rounded corners=5pt] (-72,8) rectangle (-62,-108);

        % % \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-60,8) rectangle (57, -48);
        % % \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-60,-50) rectangle (57, -108);

        % % \draw [ultra thick, draw=black, fill=green, opacity=0.15, rounded corners=20pt] (-60,-110) rectangle (70, -140);

        % % \draw [ultra thick, draw=black, fill=cyan, opacity=0.15, rounded corners=20pt] (-60,-142) rectangle (70, -160);

        % \draw [arrow] (pro1) -- (pro2);
        % \draw [arrow] (pro2) -- (filter);
        % \draw [arrow] (filter) -- (proposal_region);
        % \draw [arrow] (proposal_region) -- (surrogate);

>>>>

\begin{figure}[ht]
  \begin{center}
  %   \resizebox{.32\textwidth}{!}{
  %     \begin{tikzpicture}[node distance=1.4cm, scale=.1]
  %     \end{tikzpicture}
  %   }
    \resizebox{.8\textwidth}{!}{    
      \begin{tikzpicture}[node distance=1.2cm, scale=.1]

        % backgrounds
        \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-115, 8) rectangle (70, -108);
        \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-115, -110) rectangle (70, -138);
        \draw [ultra thick, draw=black, fill=red, opacity=0.15, rounded corners=20pt] (-115, -142) rectangle (70, -158);

        % first graph
        % private functions
        \node (n1) [train_process, xshift=-.8cm] { $\_sample\_nuisance()$  };
        \node (n2) [train_process, below of=n1] { $\_define\_objectives()$  };
        \node (n3) [decision, below of=n2, yshift=-.5cm] { $grads?$  };
        \node (n4) [train_process, left of=n3, yshift=-1cm, xshift=-1.5cm] { $\_solve\_gradients()$  };
        \node (n5) [train_process, right of=n3, yshift=-1cm, xshift=1.5cm] { $\_solve\_bo()$  };
        \node (n6) [train_process, below of=n3, yshift=-1.5cm] { $\_filter\_solutions()$  };
        \node (n7) [train_process, below of=n6] { $\_build\_boxes()$  };
        \node (n8) [decision, below of=n7] { $fit?$  };
        \node (n9) [train_process, right of=n8, yshift=-1cm, xshift=1cm] { $\_fit\_models()$  };

@@

        % add headers
        \node (impl_design) [below of=n1, yshift=2.5cm, xshift=1cm, minimum width=4cm, minimum height=1cm] {\huge{Implementation Design} };

@@
